---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
) 
```


# Awesome PyLadies' Blogs  
<!-- badges: start -->
[![Awesome](https://awesome.re/badge.svg)](https://awesome.re)
<!-- badges: end -->

## What Is This Repository About? 

It provides a curated list of awesome blogs by PyLadies and also seeks to collect information to further promote blog posts by awesome [PyLadies on Mastodon](https://botsin.space/@pyladies_bot) 🤖

To contribute to the list, please see the [contributing](CONTRIBUTING.md) guidelines ✨


## List of Blogs

Created by accessing the json files in [blogs/](blogs/)

```{r, echo = FALSE, results='asis'}
json_list <- list.files(here::here("blogs"), "json$", full.names = TRUE)
dt <- lapply(json_list, jsonlite::read_json)

invisible(
  lapply(dt, function(x){
    cat(sprintf(" - [%s](%s) by %s", 
                x$title, x$url,
                paste(sapply(x$authors, function(x) x$name), collapse=", ")),
        sep = "\n")
  })
)

#lapply(dt, function(x){
#    cat(sprintf(" - ![](%s) [%s](%s) by %s", 
#                x$photo_url, x$title, x$url,
#                paste(sapply(x$authors, function(x) x$name), collapse=", ")),
#        sep = "\n")
#  })

```

## Any Questions?

If you have any questions or suggestions, please reach out to [Cosima](mailto:contact@cosimameyer.com) or open an [issue](https://github.com/cosimameyer/awesome-pyladies-blogs/issues/new/choose).

## License

[![CC0](https://upload.wikimedia.org/wikipedia/commons/6/69/CC0_button.svg)](https://creativecommons.org/publicdomain/zero/1.0/)

## Credits

This repository relies heavily on the [Awesome R-Ladies blogs repository](https://github.com/rladies/awesome-rladies-blogs), to whom all credit goes. 

