---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
) 

library(reticulate)
```


# Awesome PyLadies' Blogs  
<!-- badges: start -->
[![Awesome](https://awesome.re/badge.svg)](https://awesome.re)
<!-- badges: end -->

## What Is This Repository About? 

It provides a curated list of awesome blogs by PyLadies and also seeks to collect information to further promote blog posts by awesome [PyLadies on Mastodon](https://botsin.space/@pyladies_bot) 🤖

To contribute to the list, please see the [contributing](CONTRIBUTING.md) guidelines ✨


## List of Blogs

Created by accessing the json files in [blogs/](blogs/).

### List of Blogs as Tiles 
```{python, echo=FALSE, eval=FALSE, results='asis'}
# TODO: Make it more beautiful 

import pandas as pd
import json
import os

directory_path = "blogs/"

# Create an empty list to store the loaded JSON data
json_data = []

# Loop through each file in the directory
for filename in os.listdir(directory_path):
    # Check if the file is a JSON file
    if filename.endswith(".json"):
        # Open the file and load the JSON data
        with open(directory_path + filename, "r") as json_file:
            data = json.load(json_file)
            json_data.append(data)

json_data.sort(key=lambda x: x["title"])


def split(lst,n):
  print(lst[i::n])
  return [lst[i::n] for i in range(n)]

# Split data into three chunks
data_splitted = list(split(json_data, 3))

# Parse data
def parse_data(data_splitted, i):
  grid_entries = []
  for entry in data_splitted[i]:
    name = entry['authors'][0]['name']
    photo_url = entry['photo_url']
    title = entry['title']
    blog_url = entry['url']
    
    grid_entry = f'<a href="{blog_url}"><img width="100" alt="Image of {name}" src="{photo_url}"><br/></a><span class="caption">{name}</span>'
    grid_entries.append(grid_entry)
  
  # Append to column if there's a different length
  length_longest_split = len(data_splitted[0])
  length_split = len(data_splitted[i])
  if length_split < length_longest_split:
    missing = length_longest_split - length_split
    grid_entries = grid_entries + (missing*[''])
    
  return grid_entries

data = {}

for i in range(len(data_splitted)):
  data[f"col_{i}"] = parse_data(data_splitted, i)
  
df = pd.DataFrame(
     data={"col_0": data["col_0"], 
           "col_1": data["col_1"],
           "col_2": data["col_2"]}
 )
 
df.columns = [''] * len(df.columns)

print(df.to_markdown(index=False))

```

```{python, echo = FALSE, results='asis', eval=TRUE}
import json
import os
import pandas as pd
directory_path = "blogs/"

# Create an empty list to store the loaded JSON data
json_data = []

# Loop through each file in the directory
for filename in os.listdir(directory_path):
    # Check if the file is a JSON file
    if filename.endswith(".json"):
        # Open the file and load the JSON data
        with open(directory_path + filename, "r") as json_file:
            data = json.load(json_file)
            json_data.append(data)

json_data.sort(key=lambda x: x['authors'][0]['name'])

header = "| | | |"
first_row = "|:-------------------------:|:-------------------------:|:-------------------------:|"

grid_entries = ""
# Parse data
count = 0
for entry in json_data:
  count += 1
  name = entry['authors'][0]['name']
  photo_url = entry['photo_url']
  title = entry['title']
  blog_url = entry['url']
  if count % 3 == 0:
    sep = '\n|'
  else:
    sep = ''
    
  
  grid_entry = f'<a href="{blog_url}"><img width="100" alt="Image of {name}" src="{photo_url}"><br></a><span class="caption">{name}</span>|{sep}'
  
  grid_entries += grid_entry
  
full_table = f"{header}\n{first_row}\n|{grid_entries}"

text = os.linesep.join([s for s in full_table.splitlines() if s])
print(text)

#print(to_be_returned)

```


### List of Blogs as List

```{r, echo = FALSE, results='asis'}
json_list <- list.files(here::here("blogs"), "json$", full.names = TRUE)
dt <- lapply(json_list, jsonlite::read_json)

invisible(
  lapply(dt, function(x){
    cat(sprintf(" - [%s](%s) by %s", 
                x$title, x$url,
                paste(sapply(x$authors, function(x) x$name), collapse=", ")),
        sep = "\n")
  })
)


#lapply(dt, function(x){
#    cat(sprintf(" - ![](%s) [%s](%s) by %s", 
#                x$photo_url, x$title, x$url,
#                paste(sapply(x$authors, function(x) x$name), collapse=", ")),
#        sep = "\n")
#  })

```

## Any Open Questions?

If you have any questions or suggestions, please reach out to [Cosima](https://linktr.ee/cosima_meyer) or open an [issue](https://github.com/cosimameyer/awesome-pyladies-blogs/issues/new/choose).

## License

[![CC0](https://upload.wikimedia.org/wikipedia/commons/6/69/CC0_button.svg)](https://creativecommons.org/publicdomain/zero/1.0/)

## Credits

This repository relies heavily on the [Awesome R-Ladies blogs repository](https://github.com/rladies/awesome-rladies-blogs), to whom all credit goes. 

